Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Model&Design Goals Update

\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a group of FL clients.
  \begin{figure}
    \centering
  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
  \caption{System Model\&Threat Model.}
  \label{fig_system}
  \end{figure}   
\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each iteration. After receiving the gradient updates from all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg. After the aggregation process, the FL server updates the global model.

\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) keeps the local dataset $d_{i}$ collected by itself. FL client $c_{i}$ uses its local dataset $d_{i}$ to update the model received from the FL server. Then it dispatches the model gradient updates back to the FL server. Meanwhile, it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.

\subsection{Threat Model}
The current system suffers from the Byzantine attacks. Malicious Byzantine client $b_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $b_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}. Byzantine client $b_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server. Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

\subsection{Design Goals}
The key objective of the proposed FLPhish scheme is to provide a robust approach to accurately resist opportunistic untargeted attacks in our Ensemble FL system. Our design goals are given as follows:

\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication costs. Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose an aggregation rules in FLPhish, FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

>>>>

\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a group of FL clients.
  \begin{figure}
    \centering
  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
  \caption{System Model\&Threat Model.}
  \label{fig_system}
  \end{figure}   
\subsubsection{{FL Server}} In each iteration, the FL server $s$ provides a global model to each client. The FL server aggregates all of the gradient updates to a global update based on FedAvg after receiving them from all of the clients. The FL server updates the global model after the aggregation process.

\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$th client in FL) is preserved by each FL client $c_i$. To update the model obtained from the FL server, the FL client $c_i$ uses its local dataset $d_i$. The model gradient updates are then sent back to the FL server. Meanwhile, it repeats the preceding steps throughout the FL process until the FL server $s$ stops transmitting new models.

\subsection{Threat Model}
Byzantine attacks are a problem in the current system. The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch untargeted Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine client $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server. Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

\subsection{Design Goals}
The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic untargeted attacks in our Ensemble FL system. The following are our design goals:

\par \textit{1)} The typical FL design has a number of flaws, including incompatibility with various deep learning models in different clients and significant communication costs. As a result, we created Ensemble FL, a novel FL architecture inspired by the idea of ensemble learning. It lowers the cost of network transfers and expands our ability to defend against Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture currently needs a robust Byzantine attack protection mechanism. We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be totally trusted. In our proposed Ensemble FL system, we describe a phishing-based approach to guard against Byzantine attacks.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose an aggregation rules in FLPhish, FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
